An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-17 paper.tex
minor changes to text in report

To show the effects of the treadmill dynamics and give an idea of the frequency
content of the actual perturbations, spectral analysis plots were created 
by averaging a spectrogram over twenty seconds in the hamming window, shown 
in Figure~\ref{fig:freq_analysis}. For all speeds, the frequency content of the
commanded and measured belt speeds were noticeably similar.  
%
\begin{figure}
  \centering
  \includegraphics{figures/frequency_analysis.pdf}
  \caption{Frequency spectrum of the treadmill belt velocity input signal
    (purple) and the recorded output velocity (blue) for average belt speeds of
    0.8, 1.2, and 1.6 m/s, respectively}
  \label{fig:freq_analysis}
\end{figure}
\section*{Results}
\subsection*{Raw Data}
%
The raw data consists of a set of ASCII tab delimited text files output from
both the ``mocap'' and ``record'' modules in D-Flow in addition to a manually
generated YAML file that contains all of the necessary meta data for the given
trial. These three files are stored in a hierarchy of directories with one
trial per directory. The directories are named in the following fashion
\verb+T001/+ where \verb+T+ stands for ``trial'' and the following three digits
are provide a unique trial identification number.

>>>>

To show the effects of the treadmill dynamics and give an idea of the frequency
content of the actual perturbations, spectral density plots were created 
by averaging a spectrogram over twenty seconds in the Hamming window, shown 
in Figure~\ref{fig:freq_analysis}. For all speeds, the frequency content of the
commanded and measured belt speeds were noticeably similar.  
%
\begin{figure}
  \centering
  \includegraphics{figures/frequency_analysis.pdf}
  \caption{Frequency spectrum of the treadmill belt velocity input signal
    (purple) and the recorded output velocity (blue) for average belt speeds of
    0.8, 1.2, and 1.6 m/s, respectively}
  \label{fig:freq_analysis}
\end{figure}
\section*{Results}
\subsection*{Raw Data}
%
The raw data consists of a set of ASCII tab delimited text files output from
both the ``mocap'' and ``record'' modules in D-Flow in addition to a manually
generated YAML file that contains all of the necessary meta data for the given
trial. These three files are stored in a hierarchy of directories with one
trial per directory. The directories are named in the following fashion
\verb+T001/+ where \verb+T+ stands for ``trial'' and the following three digits
are provide a unique trial identification number.
